\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2018-07-31 sections/introduction.tex
Split sentence into two lines
Update introduction
1. Added a better start
2. Split it into better logical sections
3. Added todos

  Microorganisms naturally occur in communities which can consist of tens of thousands of species involved in complex interactions with millions of metabolic and signaling relationships.
  Each interaction within this complex ecological network can have a positive effect, a negative effect or no effect on the species involved.
  For example, bacteria that compete for the same nutrient will have a negative impact on each other when the media is deficient in that nutrient \cite{Ghoul2016}.
  There can also be cases of cross-feeding where two species produce metabolic products that are beneficial to each other.

  The microbial interaction networks are highly dynamic, and they constantly reorganize in a varying environment.
  Even under static conditions, these interactions are often difficult to predict due to their non-linear nature \cite{Konopka2015}.
  Compounding on this complexity is the fact that these interaction networks usually involve thousands of species.
  While the species diversity is now measurable through metagenomic sequencing and other technologies, the detailed characterization of inter-species interactions still escapes our understanding.
  Knowledge of the community composition at a particular instance in time would enable us to derive partial insights into the underlying dynamics.
  The study of microbial communities using high throughput genomic surveys (such as 16S rRNA gene profiling) has become routine in the resolution of microbial diversity, abundances and associations within microbial populations \cite{Jovel2016}.
  There have recently been many large-scale data collection efforts involving soil (Earth Microbiome Project) \cite{Thompson2017}, marine (Tara Oceans Project) \cite{Zhang2015} and human-associated microbiota (Human Microbiome Project) \cite{HumanMicrobiomeProjectConsortium2012}.
  With data being acquired at exponential rates, it becomes increasingly difficult and essential to be able to extract useful knowledge from them.
  The first goal of this study is to alleviate the data-to-knowledge bottleneck by creating a comprehensive database of microbial interactions comprising of several kinds of heterogeneous data from different data sources.
  The first stage of the project will involve populating the database with associations derived from experimental predictions, literature review and raw 16S sequence data.

>>>>

  Microbiomes are ubiquitous and play an important role in biogeochemical transformations in both natural as well as man-made ecosystems.
  These microbiomes comprise several thousand different microbes interacting with each other as well as their environment often through intricate metabolic and signaling relationships.

  Each interaction within this complex ecological network can have a positive effect, a negative effect or no effect on the species involved. \todo[size=\footnotesize]{Combine with an explanation of co-occurrences}
  For example, bacteria that compete for the same nutrient will have a negative impact on each other when the media is deficient in that nutrient \cite{Ghoul2016}.
  There can also be cases of cross-feeding where two species produce metabolic products that are beneficial to each other.

  High-throughput metagenomic sequencing techniques help detect, identify and quantify a large part of the constitutive microorganisms of a microbiome.
  Even though the species diversity is now measurable through metagenomics, the detailed characterization of inter-species interactions still escapes our understanding.

  The microbial interaction networks are highly dynamic, and they constantly reorganize in a varying environment.
  Even under static conditions, these interactions are often difficult to predict due to their non-linear nature \cite{Konopka2015}.
  Compounding on this complexity is the fact that these interaction networks usually involve thousands of species.

  Knowledge of the community composition at a particular instance in time would enable us to derive partial insights into the underlying dynamics.
  The study of microbial communities using high throughput genomic surveys (such as 16S rRNA gene profiling) has become routine in the resolution of microbial diversity, abundances and associations within microbial populations \cite{Jovel2016}.

  Advances in next-generation sequencing (NGS) technologies had led to the generation of a wealth of data about these microbial populations.
  There have recently been many large-scale data collection efforts involving soil (Earth Microbiome Project) \todo[size=\footnotesize]{Don't need to mention the names, just cite} \cite{Thompson2017}, marine (Tara Oceans Project) \cite{Zhang2015} and human-associated microbiota (Human Microbiome Project) \cite{HumanMicrobiomeProjectConsortium2012}.
  With data being acquired at exponential rates, it becomes increasingly difficult and essential to be able to extract useful knowledge from them.
